---
title: "Shiny Application and Reproducible Pitch"
author: "Jia Jing Liew"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

0.  Abstract\
    In this presentation, i will discuss about New York Air Quality, through linear regression model. The measurements was done from May to September 1973, which had measured temperature(degrees F), solar radiation(lang), etc.

1.  Introduction\
    First, loading data and making sure the data class or other information

```{r}
Sys.setenv(LANGUAGE="en")
library(shiny)
library(psych)
library(ggplot2)
library(dplyr)
library(datasets)
library(plotly)
data("airquality")
a<-data.frame(airquality)
class(a)
describe(a)
dim(a)
length(unique(is.na(a)))
```

2.  Making linear regression model\
    From the before, we know that the data airquality has 6 variables. We can make some assumptions, likely "Ozone" and "Wind" has some relations(actually them haven't relation).

```{r}
am1<-lm(Ozone~Wind,a)
summary(am1)
anova(am1)

am2<-lm(Ozone~Wind+Temp,a)
summary(am2)
anova(am2)
```

3.  Ploting the graphs in bar plot Now, we know "Ozone" and "Wind" has clearly from their F values, and we are plotting the graphs

```{r}
p1<-plot_ly(a, x=a$Day, y=a$Ozone, type="bar", col="green") %>% layout(xaxis=list(title='Day'),yaxis=list(title='Ozone'))
p1

p2<-plot_ly(a, x=a$Day, y=a$Wind, type="bar") %>% layout(xaxis=list(title='Day'), yaxis=list(title='Wind'))
p2

p3<-plot_ly(a, x=a$Temp, y=a$Ozone, type="bar") %>% layout(xaxis=list(title='Temp'), yaxis=list(title='Ozone'))
p3

p4<-plot_ly(a, x=a$Temp, y=a$Wind, type="bar") %>% layout(xaxis=list(title='Temp'), yaxis=list(title='Wind'))
p4

p5<-plot_ly(a, x=a$Day, y=a$Temp, type="bar") %>% layout(xaxis=list(title='Day'), yaxis=list(title='Temp'))
p5

p<-subplot(p1, p2, p3, p4)

annotations = list(
  list(x=0.15,y=1.0,text="Day-Ozone",xref="paper",yref="paper",xanchor="center",yanchor="bottom",showarrow=FALSE),
  list(x=0.4,y=1.0,text="Day-Wind",xref="paper",yref="paper",xanchor="center",yanchor="bottom",showarrow=FALSE),
  list(x=0.65,y=1.0,text="Temp-Ozone",xref="paper",yref="paper",xanchor="center",yanchor="bottom",showarrow=FALSE),
  list(x=0.9,y=1.0,text="Temp-Wind",xref="paper",yref="paper",xanchor="center",yanchor="bottom",showarrow=FALSE))

p<-p %>%layout(annotations = annotations) 

p

```

4. Some histrograms
```{r}
hist(a$Wind, main="Daily Wind", col="lightyellow", xlim=c(0,25))

hist(a$Temp, main="Daily Wind", col="lightgreen", xlim=c(50,100))
```























